Yoghurt under stress

### 2014-09-18 wokshop_wallslip.tex
Adapt to wall slip workshop. Fix broken tex. tikzpictures re-generated for each overlay.

% Allow the usage of graphics (.jpg, .png, etc.) in the document
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,arrows.meta,shapes,backgrounds, calc, positioning, topaths,chains, intersections, decorations.markings, shapes.geometric, matrix,patterns,mindmap}
%\usetikzlibrary{positioning, patterns,topaths,chains,matrix}

\usepackage{pgfplots}
\pgfplotsset{compat=1.9}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{external}
\tikzexternalize
\tikzsetexternalprefix{fig_presentation/}
%\tikzset{external/optimize=false}
%\tikzset{external/force remake}

@@

\institute[E.N.S. Lyon]{Laboratoire de physique, Ecole Normale Supérieure de Lyon}
\title[Yoghurt under stress]{Yoghurt under stress}
\author[M. Leocmach]{Mathieu Leocmach}
\date{1st June 2014}
\titlegraphic{
	\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{NEW-Logo-ERC-OUTLINE}\quad
	\includegraphics[height=2\baselineskip]{logo_ums_grand}\quad
	\includegraphics[height=2\baselineskip]{CNRSfilaire-Q}\quad
	\includegraphics[height=2\baselineskip]{logo_ens-lyon}
	}

@@

%\includeonly{}

@@

\begin{columns}
\column{0.5\textwidth}
\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=1 by 2,
			xticklabels at=edge bottom,
			vertical sep=0,
			},
		%xmode=log,
		%xmin=1e2,xmax=3e5,
		xmin=0, xmax=20,
		scale only axis,
		width=\textwidth-4em,
		height=0.3\textwidth,
		extra tick style={grid=major},%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
		]
	\nextgroupplot[
		ymin=0, ymax=7, ylabel={pH},
		extra y ticks={4.6}, extra y tick labels={},%
		]
	\addplot+[no marks,Accent2] table[x expr={\thisrowno{0}/3600}]{Y190_cas4_gdl1.pH};
	\draw[help lines] (axis cs:0,4.6) -- (axis cs:3.88,4.6) node[pos=1, above right, font=\scriptsize] {isoelectric point $pH\approx 4.6$}  -- (axis cs:3.88,0);

@@

\begin{frame}{Linear rheology: Power law (visco)elastic solid}
\[\text{stress}\rightarrow \sigma = G \gamma\leftarrow\text{strain}\]
\[\textcolor{Accent1}{\text{storage}\rightarrow} G^\prime + \imath G^{\prime\prime} \textcolor{Accent2}{\leftarrow\text{loss}}\]
\begin{tikzpicture}
\begin{loglogaxis}[
	height=0.8\textheight,
	width=\textwidth,
	xlabel={Frequency (\si{\hertz})}, ylabel={\textcolor{Accent1}{Storage} and \textcolor{Accent2}{loss} moduli (\si{\pascal})},
	domain={6e-2:70},
	]
	\addplot[Accent1, only marks, mark=*] table{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Accent2, only marks, mark=o] table[y=LossModulus]{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Main, no marks]{300*x^0.15}  node[midway, below right] {$G^\prime\sim G^{\prime\prime}\sim f^{0.15}$};
%	\addplot+[only marks, mark=*, forget plot] table{freqsweep_Y265_cas4_GDL1.txt} node[anchor=base east] {1\%};
%	\addplot+[only marks, mark=o, forget plot] table[y=LossModulus]{freqsweep_Y265_cas4_GDL1.txt} node[anchor=base east] {1\%};
%	\addplot{590*x^0.14};
%	\addplot+[only marks, mark=*, forget plot] table{freqsweep_Y277_cas4_GDL1.25.txt} node[anchor=base east] {1.25\%};
%	\addplot+[only marks, mark=o, forget plot] table[y=LossModulus]{freqsweep_Y277_cas4_GDL1.25.txt} node[anchor=base east] {1.25\%};
%	\addplot{350*x^0.12};
%	\addplot+[only marks, mark=*, forget plot] table{freqsweep_Y275_cas4_GDL1.5.txt} node[anchor=base east] {1.5\%};
%	\addplot+[only marks, mark=o, forget plot] table[y=LossModulus]{freqsweep_Y275_cas4_GDL1.5.txt} node[anchor=base east] {1.5\%};
%	\addplot{246*x^0.1};
%	\addplot+[only marks, mark=*, forget plot] table{freqsweep_Y268_cas4_GDL2.txt} node[anchor=base east] {2\%};
%	\addplot+[only marks, mark=o, forget plot] table[y=LossModulus]{freqsweep_Y268_cas4_GDL2.txt} node[anchor=base east] {2\%};
%	\addplot{163*x^0.067};
%	\addplot+[only marks, mark=*, forget plot] table{freqsweep_Y270_cas4_GDL3.txt} node[anchor=base east] {3\%};
%	\addplot+[only marks, mark=o, forget plot] table[y=LossModulus]{freqsweep_Y270_cas4_GDL3.txt} node[anchor=base east] {3\%};
%	\addplot{109*x^0.044};
%	\addplot+[only marks, mark=*, forget plot] table{freqsweep_Y271_cas4_GDL4.txt} node[anchor=base east] {4\%};
%	\addplot+[only marks, mark=o, forget plot] table[y=LossModulus]{freqsweep_Y271_cas4_GDL4.txt} node[anchor=base east] {4\%};
%	\addplot{76*x^0.035};

\end{loglogaxis}
\end{tikzpicture}
\end{frame}

\section*{Creep and yielding}

\include{creep_beamer}

>>>>

% Allow the usage of graphics (.jpg, .png, etc.) in the document
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds, calc, positioning, topaths,chains, intersections, decorations.markings, shapes.geometric, matrix,patterns,mindmap}
%\usetikzlibrary{positioning, patterns,topaths,chains,matrix}

\usepackage{pgfplots}
\pgfplotsset{compat=1.9}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{external}
\makeatletter
\newcommand*{\overlaynumber}{\number\beamer@slideinframe}
\tikzset{
  beamer externalizing/.style={%
    execute at end picture={%
      \tikzifexternalizing{%
        \ifbeamer@anotherslide
        \pgfexternalstorecommand{\string\global\string\beamer@anotherslidetrue}%
        \fi
      }{}%
    }%
  },
  external/optimize=false
}
\let\orig@tikzsetnextfilename=\tikzsetnextfilename
\renewcommand\tikzsetnextfilename[1]{\orig@tikzsetnextfilename{#1-\overlaynumber}}
\makeatother

\tikzset{every picture/.style={beamer externalizing}}
\tikzexternalize
\tikzsetexternalprefix{fig_presentation/}
%\tikzset{external/optimize=false}
%\tikzset{external/force remake}

@@

\institute[E.N.S. Lyon]{Laboratoire de physique, Ecole Normale Sup\'{e}rieure de Lyon}
\title[Yoghurt under stress]{Yoghurt under stress}
\author[M. Leocmach]{Mathieu Leocmach}
\date{1st June 2014}
\titlegraphic{
	\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{NEW-Logo-ERC-OUTLINE}\quad
	\includegraphics[height=2\baselineskip]{logo_ums_grand}\quad
	\includegraphics[height=2\baselineskip]{CNRSfilaire-Q}\quad
	\includegraphics[height=2\baselineskip]{logo_ens-lyon}
	}

@@

%\includeonly{creep_beamer}

@@

\begin{columns}
\column{0.5\textwidth}
\tikzsetnextfilename{gelation}
\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=1 by 2,
			xticklabels at=edge bottom,
			vertical sep=0,
			},
		%xmode=log,
		%xmin=1e2,xmax=3e5,
		xmin=0, xmax=20,
		scale only axis,
		width=\textwidth-4em,
		height=0.3\textwidth,
		extra tick style={grid=major},%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-0.5em}
		]
	\nextgroupplot[
		ymin=0, ymax=7, ylabel={pH},
		extra y ticks={4.6}, extra y tick labels={},%
		]
	\addplot+[no marks,Accent2] table[x expr={\thisrowno{0}/3600}]{Y190_cas4_gdl1.pH};
	\draw[help lines] (axis cs:0,4.6) -- (axis cs:3.88,4.6) node[pos=1, above right, font=\scriptsize] {isoelectric point $pH\approx 4.6$}  -- (axis cs:3.88,0);

@@

\begin{frame}{Linear rheology: Power law (visco)elastic solid}
\[\text{stress}\rightarrow \sigma = G \gamma\leftarrow\text{strain}\]
\[\textcolor{Accent1}{\text{storage}\rightarrow} G^\prime + \imath G^{\prime\prime} \textcolor{Accent2}{\leftarrow\text{loss}}\]
\tikzsetnextfilename{power_law_rheology}
\begin{tikzpicture}
\begin{loglogaxis}[
	height=0.8\textheight,
	width=\textwidth,
	xlabel={Frequency (\si{\hertz})}, ylabel={\textcolor{Accent1}{Storage} and \textcolor{Accent2}{loss} moduli (\si{\pascal})},
	domain={6e-2:70},
	]
	\addplot[Accent1, only marks, mark=*] table{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Accent2, only marks, mark=o] table[y=LossModulus]{freqsweep_Y265_cas4_GDL1.txt};
	\addplot[Main, no marks]{300*x^0.15}  node[midway, below right] {$G^\prime\sim G^{\prime\prime}\sim f^{0.15}$};	
\end{loglogaxis}
\end{tikzpicture}
\end{frame}
